Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-03 schedule.tex
oas

Most of the related methodologies can be archived into \textbf{four} main modules, namely
\begin{inparaenum}[1)]
\item Service Standardization,
\item Decision Making Support,
\item Matching Regulation and
\item Platform Assistance,
\end{inparaenum} which are going to be explained in detail respectively.

@@

OAS  
\begin{figure}[!h]
%\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
\caption{Primary Flow of Order}
\label{fig:orderflow}
\end{figure}

>>>>

Most of the related methodologies can be archived into \textbf{four} main modules, namely
\begin{inparaenum}[1)]
\item Service standardization;
\item Decision making support;
\item Matching regulation and
\item Platform assistance,
\end{inparaenum} which are going to be explained in detail respectively.

@@

For users in Cloud Manufacturing platfrom, their main acitvities are related to orders, no matter buyer or seller role they play in. The principal flow of order is shown in \autoref{fig:orderflow}, 
\begin{figure}[!h]
\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
\caption{Principal Flow of Order}
\label{fig:orderflow}
\end{figure}
users will make many decisions for
\begin{inparaenum}[1)]
\item Order acceptance;
\item Task decomposition;
\item Task (re-)outsourscing;
\item Seller selection;
\item Manufacturing arrangement
\end{inparaenum}
and so forth.

Among these decisions, Order acceptance, Seller selection and Manufacturing arrangement can be descript as a classic order acceptance and scheduling problem, which has received increasing attention in recent years\cite{Og˘uz2010,Nobibon2011,Cesaret2012}. Task decomposition and (re-)outsourscing
